Automatic conversion of colloquial Finnish to standard Finnish

### 2015-01-26 finnormal-nodalida-2015/finnormal2015.tex
more stuffs
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58582 72bbbca6-d526-0410-a7d9-f06f51895060
more references
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58583 72bbbca6-d526-0410-a7d9-f06f51895060

There are a number of areas of research related to the task of text normalisation. Text
proofing tools, such as spelling and grammar checkers CITEXXX can be used to encourage adherence
to particular orthographic or grammatical norms. Accent and diacritic restoration CITEXXX is similar
in that it aims to bring text closer to standard orthography in order to facilitate treatment by 
automatic tools. Another related area is machine translation between different written norms of 
the same language. For example between Norwegian Bokm\aa{}l and Norwegian Nynorsk \cite{unhammer2009}.

@@

\begin{table*}
  \centering
  \begin{tabular}{|lrl|l|}
    \hline
    \textbf{Rules:} & & 1. m\"{a} $\rightarrow$ min\"{a} \\
     ~              & & 2. oon $\rightarrow$ olen \\
     ~              & & 3. (?+)nkaa $\rightarrow$ ...n kanssa \\
    \hline
  \end{tabular}
~\\
~\\
  \begin{tabular}{|l|r|l|l|}
    \hline
    \textbf{Input:} & \multicolumn{3}{l|}{M\"{a} oon Inarinkaa `I am with Inari'.} \\
    \hline
    \multirow{2}{*}{Step 1} & & M\"{a} oon Inarinkaa & apply rule 1 \\
                            & & Min\"{a} oon Inarinkaa & \\
    \hline
    \multirow{2}{*}{Step 2} & & M\"{a} oon Inarinkaa & apply rule 2 \\
                            &   & Min\"{a} oon Inarinkaa & \\
                            &   & M\"{a} olen Inarinkaa & \\
                            &   & Min\"{a} olen Inarinkaa & \\
    \hline
    \multirow{2}{*}{Step 3} &   & M\"{a} oon Inarinkaa   & apply rule 3\\
                            &   & Min\"{a} oon Inarinkaa  &\\
                            &   & M\"{a} olen Inarinkaa  &\\
                            &   & Min\"{a} olen Inarinkaa  &\\
                            &   & M\"{a} oon Inarin kanssa  &\\
                            &   & Min\"{a} oon Inarin kanssa  &\\
                            &   & M\"{a} olen Inarin kanssa  &\\
                            &   & Min\"{a} olen Inarin kanssa  &\\
    \hline
    \multirow{2}{*}{Step 4} & -4.5811 &  Min\"{a} olen Inarin kanssa & rank candidates \\
                            & -7.8174 &  Min\"{a} oon Inarin kanssa & \\
                            & -8.0941 &  M\"{a} olen Inarin kanssa & \\
                            & -8.8651&  M\"{a} oon Inarin kanssa & \\
                            & -9.2045 &  Min\"{a} olen Inarinkaa & \\
                            & -12.4408 &  Min\"{a} oon Inarinkaa & \\
                            & -12.7176 &  M\"{a} olen Inarinkaa & \\
                            & -13.4885 &  M\"{a} oon Inarinkaa & \\

>>>>

There are a number of areas of research related to the task of text normalisation. Text
proofing tools, such as spelling and grammar checkers CITEXXX can be used to encourage adherence
to particular orthographic or grammatical norms. Accent and diacritic restoration --- for example in \cite{scannell2011} --- is similar
in that it aims to bring text closer to standard orthography in order to facilitate treatment by 
automatic tools. Another related area is machine translation between different written norms of 
the same language. For example between Norwegian Bokm\aa{}l and Norwegian Nynorsk \cite{unhammer2009}.

@@

\begin{table*}
  \centering
  \begin{tabular}{|lrl|l|}
    \hline
    \textbf{Rules:} & & 1. m\"{a} $\rightarrow$ min\"{a} \\
     ~              & & 2. oon $\rightarrow$ olen \\
     ~              & & 3. (?+)nkaa $\rightarrow$ \textbackslash1n kanssa \\
    \hline
  \end{tabular}
~\\
~\\
  \begin{tabular}{|l|r|l|l|}
    \hline
    \textbf{Input:} & \multicolumn{3}{l|}{M\"{a} oon Inarinkaa `I am with Inari'.} \\
    \hline
    \multirow{2}{*}{Step 1} & & M\"{a} oon Inarinkaa & apply rule 1 \\
                            & & Min\"{a} oon Inarinkaa & \\
    \hline
    \multirow{2}{*}{Step 2} & & M\"{a} oon Inarinkaa & apply rule 2 \\
                            &   & Min\"{a} oon Inarinkaa & \\
                            &   & M\"{a} olen Inarinkaa & \\
                            &   & Min\"{a} olen Inarinkaa & \\
    \hline
    \multirow{2}{*}{Step 3} &   & M\"{a} oon Inarinkaa   & apply rule 3\\
                            &   & Min\"{a} oon Inarinkaa  &\\
                            &   & M\"{a} olen Inarinkaa  &\\
                            &   & Min\"{a} olen Inarinkaa  &\\
                            &   & M\"{a} oon Inarin kanssa  &\\
                            &   & Min\"{a} oon Inarin kanssa  &\\
                            &   & M\"{a} olen Inarin kanssa  &\\
                            &   & Min\"{a} olen Inarin kanssa  &\\
    \hline
    \multirow{2}{*}{Step 4} & -4.5811 &  Min\"{a} olen Inarin kanssa & rank candidates \\
                            & -7.8174 &  Min\"{a} oon Inarin kanssa & \\
                            & -8.0941 &  M\"{a} olen Inarin kanssa & \\
                            & -8.8651&  M\"{a} oon Inarin kanssa & \\
                            & -9.2045 &  Min\"{a} olen Inarinkaa & \\
                            & -12.4408 &  Min\"{a} oon Inarinkaa & \\
                            & -12.7176 &  M\"{a} olen Inarinkaa & \\
                            & -13.4885 &  M\"{a} oon Inarinkaa & \\
